What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-22 lda-paper.tex
more edits

\hla{
What happened in the previous maintenance or development iteration?
What were the developers working on? What was the developer in the
next cubicle working on? Which common topics and issues were dealt
with in the current release of the software? What were the topics of
the previous release? Given the requirements agreed to at the start
of the iteration did our developers work on them?  What else did they
work on?
}

@@

Topic analysis extracts groups of words from documents (commit log
comments) that are word distributions, topics, that are combined to
characterize clusters of documents. These extracted topics often
correlate with actual development topics that the developers discussed
during the development of the software project.

Topic analysis often allows for a single document, such as a commit
\hla{
message, to be related to multiple topics. This maps well to commits
to source code, which often have more than one purpose.  A topic
represents both a word distribution and a group of commit log comments
that are related to each other by their content.  In this case a topic
is a set of tokens extracted from commit messages found within a
projects source control system (SCS).
}

@@

Figure \ref{fig:lda} illustrates the kind of visualization we want to
automatically generate. We want to see topics that are unique to a
certain time period, displayed across the time axis. Those topics that
recur, or occur over a larger period are plotted continuously. In our
example we have titled each topic with a single word drawn from its word
distribution.

>>>>

\hla{ The questions that we wish to address deal with the past and
  topics of development that occurred in the past.  What happened in
  the previous iteration of a project's development?  What were the
  developers working on? What was the developer in the next cubicle
  working on? Which common topics and issues were dealt with in the
  current release of the software? What were the topics of the
  previous release? Given the requirements agreed to at the start of
  the iteration did our developers work on them?  What else did they
  work on?  }

@@

Topic analysis extracts groups of words from documents (commit log
comments) that are word distributions, topics, that are combined to
characterize clusters of documents. These extracted topics often
correlate with actual development topics that the developers discussed
during the development of the software project. 
Topic analysis often allows for a single document, such as a commit
\hla{
message, to be related to multiple topics. This maps well to commits
to source code, which often have more than one purpose.  A topic
represents both a word distribution and a group of commit log comments
that are related to each other by their content.  In this case a topic
is a set of tokens extracted from commit messages found within a
projects source control system (SCS). 
}

@@

Figure \ref{fig:lda} illustrates the kind of visualization we want to
automatically generate. We want to see topics that are unique to a
certain time period, displayed across the time axis. Those topics that
recur, or occur over a larger period are plotted continuously. In our
example we have titled each topic with a single word drawn from its
word distribution.  Given a visualization, such as this, topic
analysis can aid in partitioning a project's time-line into periods of
developer focus. By breaking apart an iteration into sets of topics
and trends (topics that recur), we may be able to recognize the
underlying software development process from these
commits. Alternatively, we can determine what particular maintenance
task was being performed at a given time.
